\newpage
\chapter{Conclusion}
    \section{Future direction}
In the future, our money management application aims to incorporate AI capabilities to analyze users' buying patterns and provide personalized recommendations. By leveraging machine learning algorithms, we can gather insights from users' transaction data, identify their spending habits, and understand their preferences.

The AI system will continuously analyze patterns and trends in users' purchasing behavior, taking into account factors such as transaction frequency, purchase categories, spending amounts, and time of purchases. By applying advanced data analysis techniques, the AI will identify correlations and patterns that may not be immediately apparent to users.

Based on these insights, the AI system will generate personalized recommendations for users, suggesting relevant products or services that align with their interests and preferences. These recommendations may include discounts, special offers, or suggestions for similar products or services that users may find appealing.

To ensure privacy and data security, the AI system will adhere to strict data protection protocols. User data will be anonymized and processed in a secure and confidential manner, with the utmost respect for user privacy.

By integrating AI-driven recommendation systems into our money management application, we aim to enhance users' financial decision-making and provide them with valuable insights and suggestions to optimize their spending habits and achieve their financial goals.

\section{Conclusion}
In conclusion, the paper presents \textit{Moneager}, a mobile application designed to provide users with a comprehensive and personalized solution for managing their financial transactions. \textit{Moneager} offers a range of features and functionalities that enable users to track their expenses, create reports, and make informed financial decisions.

Throughout the development process, various technologies and tools were utilized to ensure the effectiveness and efficiency of the application. \textit{React Native}, a TypeScript framework, served as the foundation for building native-like mobile applications for both iOS and Android platforms. The \textit{Expo} development environment streamlined the frontend development workflow, providing features such as hot reloading and over-the-air updates.

The integration of \textit{GraphQL} facilitated efficient data fetching and manipulation, reducing over-fetching and under-fetching of data. \textit{TypeScript} enhanced the development process by introducing static typing, leading to improved code quality and better maintainability. Additionally, tools like \textit{Figma} and \textit{WebStorm} played a vital role in designing and developing the user interface, ensuring a seamless and intuitive user experience.

The implementation of \textit{Moneager} demonstrated the significance of collaborative interface design and prototyping. \textit{Figma}, a cloud-based design tool, enabled designers and developers to work together in real time, resulting in a cohesive and visually appealing user interface. The integration of \textit{Apollo Studio} provided effective management, monitoring, and analysis of the GraphQL API, contributing to optimized performance and improved data delivery.

Overall, \textit{Moneager} stands out as a user-friendly and comprehensive solution for managing personal finances. By incorporating educational resources and promoting financial literacy, \textit{Moneager} aims to empower users to make informed financial decisions and achieve their financial goals. With its intuitive interface, collaborative design process, and robust backend architecture, \textit{Moneager} offers a compelling user experience for individuals seeking an efficient and accessible tool for managing their finances.

In the future, further enhancements can be made to \textit{Moneager}, such as expanding its feature set, integrating additional financial services, and incorporating advanced security measures. With continuous improvements and user feedback, \textit{Moneager} has the potential to become a leading mobile application for financial management, helping users take control of their financial well-being and achieve long-term financial stability.

In summary, \textit{Moneager} demonstrates the power of technology and innovative design in simplifying the complex task of managing personal finances. By leveraging the capabilities of \textit{React Native}, \textit{GraphQL}, and various supporting tools, \textit{Moneager} provides users with a comprehensive and personalized solution for tracking expenses, making informed financial decisions, and ultimately achieving their financial goals.
