%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% cap: intro %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Introduction}\label{cap:intro}

%%%%%%%%%%%% Section: Description %%%%%%%%%%%%
\section{Problem Statement}\label{sect:description}

\hspace{\parindent}Managing finances can be a challenge for many people, especially for those who have never received proper education on financial management. Poor financial management can lead to debt, and financial stress, which can negatively impact one's quality of life.

\hspace{\parindent}One of the biggest issues with money management is the lack of financial education. Many people have never been taught how to properly manage their finances, leading to poor spending habits, lack of savings, and accumulating debt. Without the proper knowledge and skills, it can be difficult to make informed financial decisions and plan for the future.

\hspace{\parindent}Another problem is that many people live beyond their means, which means they spend more money than they earn. This can lead to accumulating debt and struggling to make ends meet. Living beyond one's means can also prevent individuals from saving money for future expenses or emergencies.

\hspace{\parindent}Savings are important because they provide a safety net for unexpected expenses and can help individuals achieve their long-term financial goals. Having savings can also reduce financial stress and provide a sense of security. However, many people struggle with saving money due to a lack of financial education, living beyond their means, and not making saving a priority.

\hspace{\parindent}While various money management applications and resources are available, they often fail to provide a comprehensive and personalized solution. Many applications are overly complex, lacking in user-friendliness, and do not adequately consider the diverse needs and circumstances of different individuals. This can be an important factor in determining the success of an application, as users are more likely to engage with an application that is easy to navigate and visually appealing.

\hspace{\parindent}Therefore, there is a need for a mobile application that provides a user-friendly and effective solution for managing personal finances. Such an application should incorporate personalized features, provide relevant and timely financial education, and promote long-term financial stability and well-being.
\vspace*{2mm}


%%%%%%%%%%%% Section: Motivation %%%%%%%%%%%%
\newpage
\section{Proposed Solution}\label{sect:motivation}
\hspace{\parindent} The proposed application is a mobile platform designed to provide users with an intuitive and user-friendly experience for managing their finances. The user interface is designed with a focus on usability and simplicity, with clear navigation and visual elements to enhance user experience. The application aims to provide users with the necessary tools and resources to manage their finances efficiently and effectively.

\hspace{\parindent}In addition to its user-friendly interface, the application incorporates features to promote financial education and literacy. It provides users with tips and resources for saving money, investing wisely, and making informed financial decisions. This aspect of the application is particularly important, as financial literacy is crucial for individuals to make informed decisions about their financial future.

\hspace{\parindent}The proposed mobile application is unique in its comprehensive approach to managing personal finances, offering users a range of features that are tailored to their specific needs. From adding transactions and generating reports to monitoring expenses and setting savings goals, the application offers a full suite of tools and resources to help users achieve their financial goals.

\hspace{\parindent}Overall, the proposed mobile application offers a powerful combination of user-friendly design and financial education resources, making it an ideal tool for individuals seeking to improve their financial management skills and achieve their long-term financial goals.

%%%%%%%%%%% Section: Similar Solutions %%%%%%%%%%%%
\section{Similar Solutions}\label{sect:similar solutions}
\hspace{\parindent} While there are other money management applications available on the market, many of them do not offer the same level of customization and personalization as the proposed application. In addition, some applications may be difficult to use or have a steep learning curve, which can deter users from using them effectively.

\hspace{\parindent}The proposed application aims to fill this gap by providing a user-friendly interface designed with UI and UX principles in mind. This ensures that users can easily navigate the application, add transactions, generate reports, and monitor their expenses without feeling overwhelmed or frustrated.

\hspace{\parindent}Moreover, the proposed application goes beyond simply tracking expenses by also providing educational resources and tips for saving money. This is important as many people struggle with managing their finances due to a lack of financial education. By incorporating educational features, the proposed application aims to help users develop better financial habits and achieve their financial goals.


\hspace{\parindent}Many similar solutions suffer from "feature creep," where too many features are added without a clear focus on usability and user experience. This can make the application overwhelming and difficult to navigate for users, defeating the purpose of a money management tool. Our proposed mobile application addresses this issue by prioritizing a user-friendly interface and focusing on key features that are most important for effective financial management.

\hspace{\parindent}While there are other solutions available, the proposed application offers a unique and comprehensive approach to money management that prioritizes user experience and education.


\subsection{BlueCoins}
\hspace{\parindent}BlueCoins is a comprehensive money management application that offers a wide range of features for users. While it may be suitable for power users who require a high level of customization and detailed financial tracking, it may not be the ideal solution for everyone, especially those who prioritize simplicity and ease of use in their financial management applications.

\hspace{\parindent}One of the main advantages of BlueCoins is its ability to allow users to create custom categories for expenses and set limits for each category to stay within their budget. It also offers features such as transaction categorization, budget forecasting, and reports. Users can also create recurring transactions for monthly expenses such as rent or bills.

\hspace{\parindent}However, the lack of emphasis on user experience may make it less appealing to casual users who are simply looking to manage their finances in an easy and efficient way. The app may also suffer from "feature creep," where too many features are added, making it more complex and overwhelming for some users.

\hspace{\parindent}Overall, while BlueCoins is a good option for power users who require a lot of customization and detailed financial tracking, it may not be the best fit for users who prioritize a user-friendly interface and simplicity in their financial management applications.

\subsection{Money Lover}
\hspace{\parindent}Money Lover is a mobile application that allows users to manage their personal finances by tracking their expenses, creating budgets, and setting financial goals. The app offers features such as expense tracking, bill reminders, and budget planning. It also provides reports and insights to help users better understand their spending habits and financial situation.

\hspace{\parindent}Compared to BlueCoins, Money Lover places a greater emphasis on user experience, with a user-friendly interface that is easy to navigate and customize. It also offers a variety of customization options, such as the ability to choose between different themes and fonts. Additionally, Money Lover has a social feature that allows users to share expenses with friends and family, making it a useful tool for group expenses.

\hspace{\parindent}Although Money Lover is a robust application for personal finance management, it does have a heavier focus on its paid feature set. This could potentially make it less appealing to the average user who may not yet be ready to invest in additional features. 

\hspace{\parindent}Moreover, the app may be seen as contradictory to its purpose, as the expensive paid feature set may discourage users who are looking for a cost-effective and accessible solution. In comparison to other solutions, Money Lover may not be as user-friendly and intuitive, especially for those who prioritize simplicity and ease of use in their financial management applications.

\hspace{\parindent}While it is a comprehensive tool for managing personal finances, it leans more towards a paid feature set which may be less accessible for the average user. This may be a disadvantage for those who are just starting to manage their finances and are not yet willing or able to pay for additional features.



\subsection{Revolut}
\hspace{\parindent}Revolut is a financial technology company that provides a mobile application for managing finances, including money transfers, currency exchange, and investment services. The app allows users to hold and exchange money in different currencies at the interbank exchange rate, making it a popular choice for international transactions.

\hspace{\parindent}While Revolut may not be a direct competitor to the proposed money management application, it is worth mentioning as it is a popular choice among users for managing their finances. The app's user-friendly interface and innovative features have made it a popular choice among millennials and tech-savvy users.

\hspace{\parindent}One advantage of Revolut is its focus on security and fraud prevention. The app offers features such as disposable virtual cards and transaction notifications to help users detect and prevent fraudulent activities. However, one disadvantage of Revolut is its limited support for certain countries and currencies, which may be a drawback for users who require more flexibility in their financial management options.

\hspace{\parindent}Overall, while Revolut may not be a direct competitor to the proposed money management application, its success and popularity among users highlight the importance of user-friendly interfaces and innovative features in the financial technology industry.